Appendix 1: Preregistered analysis with simulated data

### 2025-04-14 preregistration.Rmd
time and folder

---
title           : "Measuring psychological ownership and identity in a Finnish blood donor context"
shorttitle      : "Donation ownership"
date            : "`r Sys.setlocale('LC_TIME', 'C'); format(Sys.time(), '%d\\\\. %B %Y')`"

@@

csl             : vox-sanguinis.csl
bibliography      : ["manuscript/references.bib", "manuscript/r-references.bib"]

>>>>

---
title           : "Measuring psychological ownership and identity in a Finnish blood donor context"
shorttitle      : "Donation ownership"
date            : "`r Sys.setlocale('LC_TIME', 'C'); format(Sys.time())`"

@@

csl             : manuscript/vox-sanguinis.csl
bibliography      : ["manuscript/references.bib", "manuscript/r-references.bib"]

### 2025-04-14 preregistration_code.Rmd
time and folder

---
title: "Appendix 1: Preregistered analysis with simulated data"
author: "Abigail Edwards, Lauri Hietajärvi and Mikko Arvas"
date: "`r Sys.time()`"
output:
  pdf_document:
    toc: yes

@@

>>>>

---
title: "Appendix 1: Preregistered analysis with simulated data"
author: "Abigail Edwards, Lauri Hietajärvi and Mikko Arvas"
date: "`r Sys.setlocale('LC_TIME', 'C'); format(Sys.time())`"
output:
  pdf_document:
    toc: yes

@@

dir.create(here("figures"))
